---
title: "{{title}}"
subtitle: "Synthesis prepared for {{meeting}}"
author: "{{author}}"
date: today
lang: "{{language}}"
format:
  docx:
    toc: false
  html:
    embed-resources: true
    toc: true
params:
  survey_dir: "../.."      # this file lives in <survey_dir>/outputs/<BODY>/
  body: "{{body}}"
  nets_path: ""            # leave empty to read nets_path from ~/.nets/config.json
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
nets_path <- params$nets_path
if (!nzchar(nets_path)) {
  home <- if (.Platform$OS.type == "windows") Sys.getenv("USERPROFILE") else path.expand("~")
  nets_path <- jsonlite::read_json(file.path(home, ".nets", "config.json"))$nets_path
}
source(file.path(nets_path, "scripts", "nets_evidence.R"))

manifest <- nets_read_manifest(params$survey_dir)
ev <- nets_ev_load(file.path(params$survey_dir, "evidence", "evidence-log.csv"), manifest)
clearance <- nets_clearance(manifest) |> filter(body == str_to_upper(params$body))

# v("E###") gives the value with its unit; cite("E###") gives its source. Every id they
# are called with is recorded in used_ids for the evidence annex; use(ids) records ids
# that a table chunk reads in some other way.
used_ids <- character()
use <- function(ids) used_ids <<- union(used_ids, ids)
v <- function(id, ...) { use(id); nets_ev_value(ev, id, ...) }
cite <- function(id, ...) { use(id); nets_ev_cite(ev, id, ...) }
```

<!--
Guidance for whoever drafts this (person or agent) — delete before sending.

* Every number comes from the evidence log, written as inline R: v("E###") for the value
  and cite("E###") for its source, each wrapped in backtick-r. Do not type values. Ids used
  through v() and cite() go into the annex automatically; call use() for any others.
* Keep "What the survey found" to evidence. Put reasoning in "Interpretation", and give
  alternative explanations where they exist.
* Say what the body can and cannot use the results for. Name comparability breaks
  (vessel, gear, echosounder, timing, coverage) plainly.
* Results for areas whose clearance is not "cleared" must not appear. The clearance
  table at the end is generated from survey.yaml.
* Adapt section emphasis to the body profile in nets-knowledge/bodies/.
-->

# Purpose

<!-- Why this synthesis is submitted, to which meeting and agenda item/terms of reference,
and what the body is asked to do with it (note, use in assessment, advise, ...). -->

# The survey in brief

<!-- Objectives, period, area covered (whole-degree extent only), effort (numbers of
stations, transect miles), methods. Keep it short and cite the report. -->

# What the survey found

<!-- Evidence only, organised by what matters to this body (stocks, species groups,
ecosystem indicators, VME encounters, ...). Every value via v()/cite(). -->

# Interpretation

<!-- What the results may mean, with the reasoning. Distinguish well-supported readings
from tentative ones and give alternatives (e.g. distribution shift vs. abundance change
vs. coverage). -->

# Limitations, uncertainty and comparability

<!-- Precision (CVs, sample sizes), coverage gaps, timing relative to earlier surveys,
changes in vessel, gear or acoustic equipment, species identification issues, and what
this means for use in time series or assessments. -->

# Implications for the work of the `r params$body`

<!-- Practical consequences: can the values extend an index series? Do they support or
question current advice? What should be monitored next? -->

# Points for consideration

<!-- Concrete, modest proposals or questions for the body. Invite discussion. -->

# Data ownership and clearance

```{r}
#| label: clearance-statement
cleared <- clearance |> filter(status %in% c("cleared", "not_required"))
pending <- clearance |> filter(!status %in% c("cleared", "not_required"))
```

The results presented here were collected under the EAF-Nansen Programme. Results for
`r if (nrow(cleared)) nets_and(cleared$area_name) else "no area"`
are presented with the agreement of the respective data owners.
`r if (nrow(pending)) paste0("Results for ", nets_and(pending$area_name), " are not included in this synthesis.") else ""`
Requests for the underlying data should be addressed to the data owners.

# Annex: evidence used {.appendix}

```{r}
#| label: evidence-annex
if (length(used_ids)) {
  knitr::kable(nets_ev_annex(ev, sort(used_ids)))
} else {
  cat("No evidence ids were used.")
}
```
